Parameterization of the responses of subarctic European vegetation to key environmental variables for ozone risk assessment

### 2022-04-13 VegOzone.tex
Rearange and rwrite last paragraph in intro

Section~\ref{sec:dam}, data and methods, includes a brief summary of the major components of the used model and its key drivers. Further more we propose a method of localization of response functions based on climate data and start and end of the growing season from satellite observed gross primary productivity (GPP). In Section~\ref{sec:do3se_results}, we present our modelling results. We discuss our results and give an outlook on how these could improve future assessments of pollution risk in Section~\ref{sec:discussion}.

%%
\section{Methods and data}
\label{sec:dam}
In this section, we first describe the used model and its key components and input data and gap filling procedure (Section~\ref{sec:do3se}). After which, we put the conditions during the growing season 2018/19 into a climatological context (Section~\ref{sec:stats}). Finally, we describe our proposed method for localization of existing Boreal parameterizations to a subarctic climate (Section~\ref{sec:localization}).

@@

\section{Climate and weather conditions}
\label{sec:stats}

@@

\begin{figure*}[t]
  \includegraphics[width=12cm]{climatediagram_box}
  %\includegraphics[width=8.3cm]{fig04}
  \caption{Climate diagram based on meteorological data for Svanvik/Pasvik (1992--2012). Ozone climatology based on ozone monitoring data at NIBIO Environment Centre Svanhovd(1986--2003). A box indicates the upper/lower quartile, whiskers the $1.5\times$ Interquartile Range (IQR), and circles outliers. The median is marked by a colored horizontal line and the mean by a triangle. Notches indicate the confidence interval around the median. (a) Monthly temperatures; (b) Monthly accumulated precipitation; (c) Monthly global radiation; (d) Monthly ozone VMR}
  \label{fig:climatediagram}
\end{figure*}

@@

\begin{figure*}[t]
  %\includegraphics[width=12cm]{fig06}
  \centering
  (a)\hspace{6cm}(b)\\
  \includegraphics[width=6cm]{temperature_signific_1.pdf}
  \includegraphics[width=6cm]{precipitation_signific_1.pdf}\\
  (c)\hspace{6cm}(d)\\
  \includegraphics[width=6cm]{global_rad_signific_1.pdf}
  \includegraphics[width=6cm]{ozone_signific_1.pdf}
  \caption{2018/19 anomalies of key environmental variables at Svanhovd displayed as percentages of days significantly deviating from climatological mean through standard deviation for each month. Negative deviations from the climatology are shown as a negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates statistical significance under the assumption of a normal distribution ($15.9\,\unit{\%}$, $30.8\,\unit{\%}$ for Precip.). (a) Temperature; (b) precipitation; (c) global irradiance; (d) ozone.}
  \label{fig:anomalies_svanvik}
\end{figure*}

@@

\section{Implications on ozone risk assessments}
\label{sec:do3se_results}

>>>>

In Section~\ref{sec:dam}, we give a brief summary of the key components and  drivers of the $\mathrm{DO_3SE}$ model that is used to assess the ozone risk. To study the influence of selected parameters on ozone risk in the subarctic, we propose a method to localize temperature response functions based on climate data and start and end of the growing season from satellite observed gross primary productivity (GPP). For the later discussion of results, we summarize climate and weather conditions of the 2018/19 growing season at our research site in Section~\ref{sec:stats}. Results of the localization and ozone risk modelling are presented in Section~\ref{sec:results}. In Section~\ref{sec:conc}, we discuss these results concerning prevailing conditions and give an outlook on how future assessments of pollution risk in the subarctic could be improved.

%%
\section{Methods}
\label{sec:dam}
In the following, we briefly describe the model used for assessing the ozone risk, its key components, input data, and gap filling procedure (Section~\ref{sec:do3se}). To study the impact of model parameters, we propose a method for parameter localization to a subarctic climate based on existing Boreal parameterizations and estimate the start and end of the growing season from satellite derived GPP (Section~\ref{sec:localization}).

@@

\section{Climate and weather conditions}
\label{sec:stats}
Here, we put the conditions during the growing season 2018/19 into a climatological context.

@@

\begin{figure*}[t]
  \includegraphics[width=12cm]{climatediagram_box}
  %\includegraphics[width=8.3cm]{fig04}
  \caption{Climate diagram based on meteorological data for Svanvik/Pasvik (1992--2012). Ozone climatology based on ozone monitoring data at NIBIO Environment Centre Svanhovd(1986--2003). A box indicates the upper/lower quartile, whiskers the $1.5\times$ Interquartile Range (IQR), and circles outliers. The median is marked by a colored horizontal line and the mean by a triangle. Notches indicate the confidence interval around the median. (a) Temperature; (b) accumulated precipitation; (c) radiant energy; (d) ozone VMR}
  \label{fig:climatediagram}
\end{figure*}

@@

\begin{figure*}[t]

  \centering
  \includegraphics[width=12cm]{anomalies}
  \caption{2018/19 anomalies of key environmental variables at Svanhovd displayed as difference from median for each month. The hatched area between indicates the IQR. (a) Temperature; (b) precipitation; (c) radiant energy; (d) ozone VMR.}
  \label{fig:anomalies_svanvik}
\end{figure*}

@@

\subsection{Implications on ozone risk assessments}
\label{subsec:do3se_results}
